\instruct{Kneel and quietly make these prayers.}
\begin{multicols}{2}
	Pater noster, qui es in cælis, sanctificétur nomen tuum: advéniat regnum tuum: fiat volúntas tua, sicut in cælo et in terra. Panem nostrum quotidiánum da nobis hódie: et dimítte nobis débita nostra, sicut et nos dimíttimus debitóribus nostris: et ne nos indúcas in tentatiónem: sed líbera nos a malo.
	
	\columnbreak
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
\end{multicols}

\begin{multicols}{2}
	Ave María, grátia plena; Dóminus tecum: benedícta tu in muliéribus, et benedíctus fructus ventris tui Jesus. Sancta María, Mater Dei, ora pro nobis peccatóribus, nunc et in hora mortis nostræ. Amen.
	
	\columnbreak
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
\end{multicols}

\gregorioscore{converte_nos.gabc}

\instruct{All stand.}

\gregorioscore{deus_in_adjutorium.gabc}

\instruct{Sing together, making a profound bow toward the altar for the verse.}

\gregorioscore{gloria_patri.gabc}

\instruct{From the third Sunday before Lent until Easter, sing this instead of \enquote{Alleluia}:}

\gregorioscore{laus_tibi_domine.gabc}

\instruct{Turn to the commons for the antiphon then to the psalter for the psalms.}

\instruct{After the psalms have been sung, the lector will read the appointed chapter. All respond:}

\gregorioscore{deo_gratias.gabc}

\instruct{Turn to the commons, or if specified the propers, and sing the hymn.}

\gregorioscore{commons/ot/compline/versicle.gabc}

\instruct{Then turn to the commons or propers for the antiphon.}

\instruct{All kneel as the precantor and succentor sing antiphonally:}

\gregorioscore{kyrie.gabc}

\instruct{Make this prayer quietly.}

\begin{multicols}{2}
	Pater noster, qui es in cælis, sanctificétur nomen tuum: advéniat regnum tuum: fiat volúntas tua, sicut in cælo et in terra. Panem nostrum quotidiánum da nobis hódie: et dimítte nobis débita nostra, sicut et nos dimíttimus debitóribus nostris.
	
	\columnbreak
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us.
\end{multicols}

\gregorioscore{et_ne_nos.gabc}

\instruct{The congregation recites together.}

\begin{multicols}{2}
	Confíteor Deo omnipoténti et ómnibus Sanctis, quia peccávi nimis, cogitatióne, verbo et ópere: mea culpa, mea culpa, mea máxima culpa. Ídeo precor beátam Maríam semper Vírginem, beátum Michaélem Archángelum, beátum Joánnem Baptístam, sanctos Apóstolos Petrum et Paulum, et omnes Sanctos, oráre pro me ad Dóminum Deum nostrum.
	
	\columnbreak
	
	I confess to almighty God and to all the Saints that I have sinned greatly in thought, word, and deed: through my fault, through my fault, through my most grievous fault. Therefore I beseech blessed Mary ever-Virgin, blessed Michael the Archangel, blessed John the Baptist, the holy Apostles Peter and Paul, and all the Saints to pray for me to the Lord our God.
\end{multicols}

\instruct{The minister alone continues;}

\begin{multicols}{2}
	 Misereátur nostri omnípotens Deus, et dimíssis peccátis nostris, perdúcat nos ad \GreCross{17} vitam ætérnam. Amen.
	 
	 \columnbreak
	 
	 May almighty God have mercy upon us, and forgive us all our sins, and bring us to \GreCross{17} everlasting life. Amen.
\end{multicols}

\gregorioscore{vespers_preces_2.gabc}

\instruct{All stand.}

\instruct{The minister will pray the collect of the day in its proper place:}

\gregorioscore{oremus.gabc}

\instruct{Turn to the proper anthem of the Blessed Virgin Mary.}

\skiplines{0.5}

\gregorioscore{conclusion.gabc}

\instruct{Kneel and make these prayers quietly.}

\begin{multicols}{2}
	Pater noster.
	
	\columnbreak
	
	Our Father.
\end{multicols}

\begin{multicols}{2}
	Ave María.
	
	\columnbreak
	
	Hail Mary.
\end{multicols}

\begin{multicols}{2}
	Credo in Deum, Patrem omnipoténtem, Creatórem cæli et terræ.
	Et in Jesum Christum, Fílium ejus únicum, Dóminum nostrum: qui concéptus est de Spíritu Sancto, natus ex María Vírgine, passus sub Póntio Piláto, crucifíxus, mórtuus, et sepúltus: descéndit ad ínferos; tértia die resurréxit a mórtuis; ascéndit ad cælos; sedet ad déxteram Dei Patris omnipoténtis: inde ventúrus est judicáre vivos et mórtuos.
	Credo in Spíritum Sanctum, sanctam Ecclésiam cathólicam, Sanctórum communiónem, remissiónem peccatórum, carnis resurrectiónem, vitam ætérnam. Amen.
	
	\columnbreak
	
	I believe in God the Father almighty, creator of heaven and earth, and in Jesus Christ, his only Son, our Lord, who was conceived from the Holy Spirit and born of the Virgin Mary, who suffered under Pontius Pilate, was crucified, died, and was buried: he descended into hell, rose again from the dead on the third day, ascended into heaven and is seated at the right hand of God the Father almighty, who will come again to judge the living and the dead. I believe in the Holy Spirit, the holy catholic Church, the communion of the Saints, the remission of sins, the resurrection of the body, and the life everlasting. Amen.
\end{multicols}