\documentclass[17pt,twoside]{extreport} %%% add 17pt
\usepackage{moresize}
\usepackage{fontspec}
\usepackage{aeguill}
\usepackage{titlesec}
\usepackage[maxlevel=3]{csquotes}
\usepackage{lettrine}
\usepackage{xifthen}
\usepackage{yfonts}
\usepackage{parskip}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{hanging}
\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage[twoside]{geometry}
\usepackage{multicol}

\setlength{\columnseprule}{0.1pt}
\setlength{\columnsep}{1.5em}

\gredefsizedsymbol{GreCross}{greextra}{Cross}
\gredefsizedsymbol{GreStarHeight}{greextra}{StarHeight}
\gredefsizedsymbol{greABar}{greextra}{ABar}
\gredefsizedsymbol{greVBar}{greextra}{VBar}
\gredefsizedsymbol{greRBar}{greextra}{RBar}

\gresetspecial{R/}{\textcolor{red}{\Rbar{}}}
\gresetspecial{V/}{\textcolor{red}{\Vbar{}}}
\gresetspecial{+}{\textcolor{red}{\GreCross{17}}}
\gresetspecial{*}{\textcolor{red}{\GreStarHeight{17}}}

\grechangestaffsize{30}
\grechangedim{abovelinestextheight}{0.25cm}{fixed}
\grechangedim{spacebeneathtext}{0.5cm}{fixed}

%%% FORMATTING %%%
\newcommand{\greformat}[1]{\textcolor{red}{\textbf{#1}}}
\newcommand{\skiplines}[1]{\vspace*{#1\baselineskip}}
\newcommand{\scoreskip}[0]{\skiplines{0}}
\newcommand{\instruct}[1]{\textcolor{red}{\textit{#1}}}
\newcommand{\greant}[1]{\greannotation{#1. \color{red}\textbf{Ant.}}}
\newcommand{\breakhere}[0]{}

\let\grescore\gregorioscore
\renewcommand{\gregorioscore}[1]{\scoreskip\grescore{#1}}

\let\gresnip\gabcsnippet
\renewcommand{\gabcsnippet}[1]{\gresnip{#1}}

%%% DIVISIONS %%%
\makeatletter
\newcommand{\vepart}[1]{%
	\clearpage%
	\centerline{\LARGE \selectfont \textbf{#1}}%
	\skiplines{0.5}
}%
\makeatother

\makeatletter
\newcommand{\vechapter}[1]{%
	\centerline{\large \selectfont #1}%
	\skiplines{0.5}
}%
\makeatother

\makeatletter
\newcommand{\vesection}[1]{%
	\skiplines{0.5}%
	\centerline{\selectfont \textbf{#1}}%
	%\nopagebreak[4]%
}%
\makeatother

\makeatletter
\newcommand{\veheading}[1]{%
	\skiplines{0.5}%
	\centerline{\selectfont \textit{#1}}%
	%\nopagebreak[4]%
}%
\makeatother

%%% HELPERS %%%
\makeatletter
\newcommand{\gloria}[0]{%
	Glória Patri, et Fílio, * et Spirítui Sancto.
	
	Sicut erat in princípio, et nunc, et semper, * et in s\'{æ}cula sæculórum. Amen.
}%
\makeatother

\begin{document}
	\raggedbottom
	\newgeometry{margin=0pt}
	\begin{titlepage}
		\vspace*{\fill}
		\centerline{\Huge\selectfont VESPERALE}
		
		\vspace*{0.5\baselineskip}
		
		\centerline{\large\selectfont OF THE}
		
		\vspace*{0.5\baselineskip}
		
		\centerline{\Large\selectfont HOLY ROMAN CHURCH}
		
		\vspace*{\fill}
		
		\centerline{\LARGE\selectfont VESPERS AND COMPLINE}
		
		\vspace*{1\baselineskip}
		
		\centerline{\large\selectfont ACCORDING TO THE USE OF SARUM}
		
		
		\vspace*{\fill}
		
		\centerline{\normalsize\selectfont ARRANGED FOR USE OF THE KENT STATE UNIVERSITY PARISH}
		
		\vspace*{\baselineskip}
		
		\centerline{\normalsize\selectfont MMXXIII}
		
		\vspace*{\fill}
	\end{titlepage}

	\newgeometry{top=0.25in,bottom=0.25in,inner=0.25in,outer=0.5in,includefoot}
	
	\pagenumbering{arabic}
	\gresetinitiallines{0}
	
	\vepart{Ordo for Vespers}
	\input{vespers_ordo}
	
	\vepart{Ordo for Compline}
	\input{compline_ordo}
	
	\vepart{Psalter}
	\vechapter{Sunday at Second Vespers}
	\input{sunday/ii/sunday_ii}
	
	\clearpage
	\vechapter{Monday at Vespers}
	\input{monday/monday}
	
	\clearpage
	\vechapter{Tuesday at Vespers}
	\input{tuesday/tuesday}
	
	\clearpage
	\vechapter{Wednesday at Vespers}
	\input{wednesday/wednesday}
	
	\clearpage
	\vechapter{Thursday at Vespers}
	\input{thursday/thursday}
	
	\clearpage
	\vechapter{Friday at Vespers}
	\input{friday/friday}
	
	\clearpage
	\vechapter{Sunday at First Vespers}
	\input{sunday/i/sunday_i}
	
	\clearpage
	\vechapter{At Compline}
	\input{compline}
	
	\clearpage
	\vepart{Commons of the Seasons}
	\vechapter{Advent I}
	\vesection{At Vespers}
	\input{commons/advent/1/vespers}
	
	\clearpage
	\vesection{At Compline}
	\input{commons/advent/1/compline}
	
	\clearpage
	\vechapter{Advent II}
	\vesection{At Vespers}
	\input{commons/advent/2/vespers}
	
	\clearpage
	\vesection{At Compline}
	\input{commons/advent/2/compline}
	
	\clearpage
	\vechapter{Christmastide}
	\vesection{At Vespers}
	\input{commons/christmas/vespers}
	
	\clearpage
	\input{commons/christmas/compline}
	
	\clearpage
	\vechapter{Ordinary Time}
	\vesection{Sunday at Second Vespers}
	\input{commons/ot/sunday_i}
	
	\clearpage
	\vesection{Monday at Vespers}
	\input{commons/ot/monday}
	
	\clearpage
	\vesection{Tuesday at Vespers}
	\input{commons/ot/tuesday}
	
	\clearpage
	\vesection{Wednesday at Vespers}
	\input{commons/ot/wednesday}
	
	\clearpage
	\vesection{Thursday at Vespers}
	\input{commons/ot/thursday}
	
	\clearpage
	\vesection{Friday at Vespers}
	\input{commons/ot/friday}
	
	\clearpage
	\vesection{Sunday at First Vespers}
	\input{commons/ot/saturday}
	
	\clearpage
	\vesection{At Compline}
	\input{commons/ot/compline}
	
	\clearpage
	\vechapter{Lent I}
	\instruct{These commons begin on the first Sunday of Lent until the third Sunday. Afterwards, everything is from the propers for each week.}
	
	\vesection{At Vespers}
	\input{commons/lent/vespers}
	
	\clearpage
	\vesection{At Compline}
	\input{commons/lent/compline}
	
	\clearpage
	\vechapter{Easter}
	\instruct{These commons are sung from the Second Sunday of Easter until the Ascension.}
	
	\vesection{Sunday at First Vespers}
	\input{commons/easter/first_vespers}
	
	\clearpage
	\vesection{Sunday at Second Vespers and Feria at Vespers}
	\input{commons/easter/vespers}
	
	\clearpage
	\vesection{At Compline}
	\input{commons/easter/compline}
	
	\clearpage
	\vepart{Propers of the Seasons} 
	\input{propers/seasons}
	
	\clearpage
	\vepart{Propers of Time} % Sundays of august, september, october, november
	\vechapter{Greater Advent}
	\input{propers/advent/o_antiphons}
	
	\clearpage
	\vepart{Commons of the Saints}
	
	\clearpage
	\vepart{Propers of the Saints}
	
	\clearpage
	\gresetinitiallines{0}
	\vepart{Anthems of the Blessed Virgin Mary}
	\vechapter{Alma Redemptoris Mater}
	
	\veheading{Solemn Tone.}
	
	\gregorioscore{anthems/alma_solemn.gabc}
	
	\veheading{Simple Tone.}
	
	\gregorioscore{anthems/alma_simple.gabc}
	
	\skiplines{1}
	
	\instruct{In Advent:}
	
	\gregorioscore{anthems/advent_versicle.gabc}
	
	\instruct{But in Christmastide instead:}
	
	\gregorioscore{anthems/christmas_versicle.gabc}
	
	\clearpage
	\vechapter{Salve Regina}
	\veheading{Solemn Tone.}
	\gregorioscore{anthems/salve_solemn.gabc}
	
	\veheading{Simple Tone.}
	
	\gregorioscore{anthems/salve_simple.gabc}
	
	\skiplines{1}
	
	\gregorioscore{anthems/ot_versicle.gabc}
	
	\clearpage
	\vechapter{Ave Regina Caelorum}
	\veheading{Solemn Tone.}
	
	\gregorioscore{anthems/lent_solemn.gabc}
	
	\veheading{Simple Tone.}
	
	\gregorioscore{anthems/lent_simple.gabc}
	
	\skiplines{1}
	
	\gregorioscore{anthems/lent_versicle.gabc}
	
	\clearpage
	\vechapter{Regina Caeli}
	
	\veheading{Solemn Tone.}
	
	\gregorioscore{anthems/easter_solemn.gabc}
	
	\veheading{Simple Tone.}
	
	\gregorioscore{anthems/easter_simple.gabc}
	
	\skiplines{1}
	
	\gregorioscore{anthems/easter_versicle.gabc}
\end{document}