\instruct{Kneel and quietly make these prayers.}
\begin{multicols}{2}
	 Pater noster, qui es in cælis, sanctificétur nomen tuum: advéniat regnum tuum: fiat volúntas tua, sicut in cælo et in terra. Panem nostrum quotidiánum da nobis hódie: et dimítte nobis débita nostra, sicut et nos dimíttimus debitóribus nostris: et ne nos indúcas in tentatiónem: sed líbera nos a malo.
	
	\columnbreak
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
\end{multicols}

\begin{multicols}{2}
	Ave María, grátia plena; Dóminus tecum: benedícta tu in muliéribus, et benedíctus fructus ventris tui Jesus. Sancta María, Mater Dei, ora pro nobis peccatóribus, nunc et in hora mortis nostræ. Amen.
	
	\columnbreak
	
	Hail Mary, full of grace, the Lord is with thee. Blessed art thou among women and blessed is the fruit of thy womb, Jesus. Holy Mary, Mother of God, pray for us sinners now and at the hour of our death. Amen.
\end{multicols}

\instruct{Stand as the minister begins.}

\gregorioscore{deus_in_adjutorium.gabc}

\instruct{Sing together, making a profound bow toward the altar for the verse.}

\gregorioscore{gloria_patri.gabc}

\instruct{From the third Sunday before Lent until Easter, sing this instead of \enquote{Alleluia}:}

\gregorioscore{laus_tibi_domine.gabc}

\instruct{Sing the psalms and their antiphons indicated in the psalter, unless other psalms or antiphons have been indicated in the propers or commons.}

\instruct{After the psalms have been sung, the lector will read the appointed chapter. All respond:}

\gregorioscore{deo_gratias.gabc}

\instruct{If a responsory is prescribed in the propers or commons, it is sung now.}

\instruct{Turn to the commons, or if specified the propers, and sing the hymn, versicle, and \enquote{Magnificat} with its antiphon.}

\instruct{If the preces are not to be prayed, skip to pp.} \pageref{skip_vespers_preces}.
		
		\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
		
		\vesection{Preces}
		
		\instruct{On ferial days, except from December 17 until after the octave of the Epiphany and during Easter, these preces are prayed.}
		
		\instruct{All kneel as the precantor and succentor sing antiphonally:}
		
		\gregorioscore{kyrie.gabc}
		
		\instruct{Make this prayer quietly.}
		
		\begin{multicols}{2}
			Pater noster, qui es in cælis, sanctificétur nomen tuum: advéniat regnum tuum: fiat volúntas tua, sicut in cælo et in terra. Panem nostrum quotidiánum da nobis hódie: et dimítte nobis débita nostra, sicut et nos dimíttimus debitóribus nostris.
			
			\columnbreak
			
			Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us.
		\end{multicols}
	
		\gregorioscore{et_ne_nos.gabc}
		
		\gregorioscore{vespers_preces.gabc}
		
		\instruct{The congregation recites together this psalm without note:}
		
		\input{psalter/51}
		
		\gregorioscore{vespers_preces_2.gabc}
		
		\instruct{All stand.}
		
		\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\label{skip_vespers_preces}
\instruct{The minister will pray the collect of the day in its proper place:}

\gregorioscore{oremus.gabc}

\gregorioscore{conclusion.gabc}

\instruct{Kneel and quietly make this prayer.}
\begin{multicols}{2}
	Pater noster, qui es in cælis, sanctificétur nomen tuum: advéniat regnum tuum: fiat volúntas tua, sicut in cælo et in terra. Panem nostrum quotidiánum da nobis hódie: et dimítte nobis débita nostra, sicut et nos dimíttimus debitóribus nostris: et ne nos indúcas in tentatiónem: sed líbera nos a malo.
	
	\columnbreak
	
	Our Father, who art in heaven, hallowed be thy name. Thy kingdom come. Thy will be done on earth as it is in heaven. Give us this day our daily bread and forgive us our trespasses as we forgive those who trespass against us. And lead us not into temptation but deliver us from evil.
\end{multicols}