\veheading{Psalm 132. \textit{Momento Domine}. \textit{cxxxi}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	Lord, remember David * and all his trouble.
	
	How he sware unto the Lord * and vowed a vow unto the Almighty God of Jacob.
	
	I will come within the tabernacle of mine house * nor climb into my bed.
	
	I will not suffer mine eyes to sleep, nor mine eyelids to slumber * neither the temples of my head to take any rest.
	
	Until I found out a place for the temple of the Lord * a habitation for the mighty God of Jacob.
	
	Lo, we heard of the same at Ephrata * and found it in the wood.
	
	We will go into his tabernacle * and fall low on our knees before his footstool.
	
	Arise, O Lord, into thy resting place * thou, and the ark of thy strength.
	
	Let thy priests be clothed with righteousness * and let thy saints sing with joyfulness.
	
	For thy servant David's sake * turn not away the presence of thy Anointed.
	
	The Lord hath made a faithful oath unto David * and he shall not shrink from it.
	
	Of the fruit of thy body * shall I set upon thy seat.
	
	If thy children will keep my covenant, and my testimonies that I shall learn them * their children also shall sit upon thy throne forevermore.
	
	For the Lord hath chosen Zion to be a habitation for himself * he hath longed for her.
	
	This shall be my rest forever * here will I dwell, for I have a delight therein.
	
	I will bless her victuals with increase * and will satisfy her poor with bread.
	
	I will deck her priests with health * and her saints shall rejoice and sing.
	
	There shall I make the horn of David to flourish * I have ordained a lantern for mine Anointed.
	
	As for his enemies, I shall clothe them with shame * but upon himself shall his crown flourish.
	
	\gloria{}
\end{multicols}