\veheading{Psalm 117. \textit{Laudate Nomen}. \textit{cxxxiv}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	O praise the Lord, laud ye the Name of the Lord * praise it, O ye servants of the Lord.
	
	Ye that stand in the house of the Lord * in the courts of the house of our God.
	
	O praise the Lord, for the Lord is gracious * O sing praises unto his Name, for it is lovely.
	
	For why? the Lord hath chosen Jacob unto himself * and Israel for his own possession.
	
	For I know that the Lord is great * and that our Lord is above all gods.
	
	Whatsoever the Lord pleased, that did he in heaven, and in earth * and in the sea, and in all deep places.
	
	He bringeth forth the clouds from the ends of the world * and sendeth forth lightnings with the rain, bringing the winds out of his treasures.
	
	He smote the firstborn of Egpyt * both of man and beast.
	
	He hath sent tokens and wonders into the midst of thee, O thou land of Egypt * upon Pharaoh, and all his servants.
	
	He smote diverse nations * and slew mighty kings.
	
	Sehon king of Amorites, and Og the king of Basan * and all the kingdoms of Canaan.
	
	And gave their land to be a heritage * even a heritage unto Israel his people.
	
	Thy Name, O Lord, endureth forever * so doth thy memorial, O Lord, from one generation to another.
	
	As for the images of the heathen, they are but silver and gold * the work of men's hands.
	
	They have mouths, and speak not * eyes have they, but they see not.
	
	They have ears, and yet they hear not * neither is there any breath in their mouths.
	
	They that make them are like unto them * and so are all they that put their trust in them.
	
	Praise the Lord, ye house of Israel * praise the Lord, ye house of Aaron.
	
	Praise the Lord, ye house of Levi * ye that fear the Lord, praise the Lord.
	
	Praised be the Lord out of Zion, who dwelleth at Jerusalem.
	
	\gloria{}
\end{multicols}