\veheading{Psalm 136. \textit{Confitemini}. \textit{cxxxv}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	O give thanks unto the Lord, for he is gracious * and his mercy endureth forever.
	
	O give thanks unto the God of all gods * for his mercy endureth forever.
	
	O thanks the Lord of all lords * for his mercy endureth forever.
	
	Who by his excellent wisdom made the heavens * for his mercy endureth forever.
	
	Who hath made great lights * for his mercy endureth forever.
	
	The sun to rule the day * for his mercy endureth forever.
	
	The moon and the stars to govern the night * for his mercy endureth forever.
	
	Who smote Egypt, with their firstborn * for his mercy endureth forever.
	
	And brought out Israel from among them * for his mercy endureth forever.
	
	With a mighty hand and stretched out arm * for his mercy endureth forever.
	
	Who divided the Red Sea in two parts * for his mercy endureth forever.
	
	And made Israel to go through the midst of it * for his mercy endureth forever.
	
	But as for Pharoah and his host, he overthrew them in the Red Sea * for his mercy endureth forever.
	
	Who led his people through the wilderness * for his mercy endureth forever.
	
	Who smote great kings * for his mercy endureth forever.
	
	Yea, and slew mighty kings * for his mercy endureth forever.
	
	Sehon king of the Amorites * for his mercy endureth forever.
	
	And Og the king of Basan * for his mercy endureth forever.
	
	And gave away their land for a heritage * for his mercy endureth forever.
	
	Even for a heritage unto Israel his servant * for his mercy endureth forever.
	
	Who remembered us when we were in trouble * for his mercy endureth forever.
	
	And hath delivered us from our enemies * for his mercy endureth forever.
	
	Who giveth food to all flesh * for his mercy endureth forever.
	
	O give thanks unto the God of heaven * for his mercy endureth forever.
	
	O give thanks unto the Lord of lords * for his mercy endureth forever.
	
	\gloria{}
\end{multicols}