\veheading{Psalm 139. \textit{Domine probasti}. \textit{cxxxviii}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	O Lord, thou hast searched me out, and known me * thou knowest my down-sitting, and mine up-rising; thou understandest my thoughts long before.
	
	Thou art about my path, and about my bed * and spiest out all my ways.
	
	For lo, there is not a word in my tongue * but thou, O Lord, knowest it altogether.
	
	Thou hast fashioned me behind and before * and laid thine hand upon me.
	
	Such knowledge is too wonderful and excellent for me * I cannot attain unto it.
	
	Whither shall I go then from thy Spirit * or whither shall I go then from thy presence?
	
	If I climb up into heaven, thou art there * if I go down to hell, thou art there also.
	
	If I take the wings of the morning * and remain in the uttermost parts of the sea.
	
	Even there also shall thy hand lead me * and thy right hand shall hold me.
	
	If I say, Peradventure the darkness shall cover me * then shall my night be turned to day.
	
	Yea, the darkness is no darkness with thee, but the night is as clear as the day * the darkness and light to thee are both alike.
	
	For my reins are thine * thou hast covered me in my mother's womb.
	
	I will give thanks unto thee, for I am fearfully and wonderfully made * marvelous are thy works, and that my soul knoweth right well.
	
	My bones are not hid from thee * though I be made secretly, and fashioned beneath in the earth.
	
	Thine eyes did see my substance, yet being imperfect * and in thy book were all my members written.
	
	Which day by day were fashioned * when as yet there was none of them.
	
	How dear are thy counsels unto me, O God * O how great is the sum of them.
	
	If I tell them, they are more in number than the sand * when I wake up, I am present with thee.
	
	Wilt thou not slay the wicked, O God * depart from me, ye bloodthirsty men.
	
	For they speak unrighteously against thee * and thine enemies take thy Name in vain.
	
	Do not I hate them, O Lord, that hate thee * and am not I grieved with those that rise up against thee?
	
	Yea, I hate them right sore * even as though they were mine enemies.
	
	Try me, O God, and seek the ground of my heart * prove me, and examine my thoughts.
	
	Look well if there be any way of wickedness in me * and lead me in the way everlasting.
	
	\gloria{}
\end{multicols}