\veheading{Psalm 144. \textit{Benedictus Dominus}. \textit{cxliii}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	Blessed be the Lord my strength * who teacheth my hands to war, and my fingers to fight.
	
	My hope and my fortress, my castle and deliverer, my defender in whom I trust * who subdueth my people that is under me.
	
	Lord, what is man, that thou hast such respect unto him * or the son of man, that thou so regardest him?
	
	Man is like a thing of nought * his time passeth away like a shadow.
	
	Bow thy heavens, O Lord, and come down * touch the mountains, and they shall smoke.
	
	Cast forth thy lightning, and tear them * shoot out thine arrows, and consume them.
	
	Send down thine hand from above * deliver me, and take me out of the great waters, from the hand of strange children.
	
	Whose mouth talketh of vanity * and their right hand is a right hand of wickedness.
	
	I will sing a new song unto thee, O God * and sing praises unto thee upon a ten-stringed lute.
	
	Thou hast given victory unto kings * and hast delivered David thy servant from the peril of the sword.
	
	Save me, and deliver me from the hand of strange children * whose mouth talketh of vanity, and their right hand is a right hand of iniquity.
	
	That our sons may grow up as the young plants * and that thou daughters may be as the polished corners of the temple.
	
	That our garners may be full and plenteous with all manner of store * that our sheep may bring forth thousands and ten thousands in our streets.
	
	That our oxen may be strong to labor, that there be no decay * no leading into captivity, and no complaining in our streets.
	
	Happy are the people that are in such a case * yea, blessed are the people who have the Lord for their God.
	
	\gloria{}
\end{multicols}