\veheading{Psalm 145. \textit{Exaltabo te Deus}. \textit{cxliv}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	I will magnify thee, O God, my King * and I will praise thy Name forever and ever.
	
	Every day will I give thanks unto thee * and praise thy Name forever and ever.
	
	Great is the Lord, and marvelous, worthy to be praised * and there is no end of his greatness.
	
	One generation shall praise thy works unto another * and declare thy power.
	
	As for me, I will be talking of thy worship * thy glory, thy praise, and wondrous works.
	
	So that men shall speak of the might of thy marvelous acts * and I will also tell of thy greatness.
	
	The memorial of thine abundant kindness shall be shewed * and men shall sing of thy righteousness.
	
	The Lord is gracious and merciful * long-suffering, and of great goodness.
	
	The Lord is loving unto every man * and his mercy is over all his works.
	
	All thy works praise thee, O Lord * and thy saints give thanks to thee.
	
	They shew the glory of thy kingdom * and talk of thy power.
	
	That thy power, thy glory, and mightiness of thy kingdom * might be known unto men.
	
	Thy kingdom is an everlasting kingdom * and thy dominion endureth throughout all ages.
	
	The Lord upholdeth all such as fall * and lifteth up all those that are down.
	
	The eyes of all wait upon thee, O Lord * and thou givest them their meat in due season.
	
	Thou openest thine hand * and fillest all things living with plenteousness.
	
	The Lord is righteous in all his ways * and holy in all his works.
	
	The Lord is night unto all them that call upon him * yea, all such as call upon him faithfully.
	
	He will fulfill the desire of them that fear him * he also will hear their cry, and will help them.
	
	The Lord preserveth all them that love him * but scattereth abroad all the ungodly.
	
	My mouth shall speak the praise of the Lord * and let all flesh give thanks unto his holy Name forever and ever.
	
	\gloria{}
\end{multicols}