\veheading{Psalm 51. \textit{Miserere mei Deus}. \textit{l}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	Have mercy upon me, O God, after thy great goodness * according to the multitude of thy mercies do away mine offenses.
	
	Wash me thoroughly from my wickedness * and cleanse me from my sin.
	
	For I acknowledge my faults * and my sin is ever before me.
	
	Against thee only have I sinned, and done this evil in thy sight * that thou mighest be justified in thy saying, and clear when thou art judged.
	
	Behold, I was shapen in wickedness * and in sin hath my mother conceived me.
	
	But lot, thou requirest truth in the inward parts * and shalt make me to understand wisdom secretly.
	
	Thou shalt purge me with hyssop, and I shall be clean * thou shalt wash me, and I shall be whiter than snow.
	
	Thou shalt make me hear of joy and gladness * that the bones which thou hast broken may rejoice.
	
	Turn thy faces from my sins * and put out all my misdeeds.
	
	Make me a clean heart, O God * and renew a right spirit within me.
	
	Cast me not away from thy presence * and take not thy holy Spirit from me.
	
	O give me the comfort of thy help again * and establish me with thy free Spirit.
	
	Then shall I teach thy ways unto the wicked * and sinners shall be converted unto thee.
	
	Deliver me from blood-guiltiness, O God, thou that art the God of my health * and my tongue shall sing of thy righteousness.
	
	Thou shalt open my lips, O Lord * and my mouth shall shew thy praise.
	
	For thou desirest no sacrifice, else would I give it thee * but thou delightest not in burnt-offerings.
	
	The sacrifice of God is a troubled spirit * a broken and contrite heart, O God, shalt thou not despise.
	
	O be favorable and gracious under Zion * build thou the walls of Jerusalem.
	
	Then shalt thou be pleased with the sacrifice of righteousness, with the burnt-offerings and oblations * then shall they offer young bullocks upon thine altar.
	
	\gloria{}
\end{multicols}