\veheading{Psalm 91. \textit{Qui habitat}. \textit{xc}.}
\begin{multicols}{2}
	\interlinepenalty=10000
	
	Whoso dwelleth under the defense of the most High * shall abide under the shadow of the Almighty.
	
	I will say unto the Lord, Thou art my hope and my stronghold * my God, in him will I trust.
	
	For he shall deliver thee from the snare of the hunter * and from the noisome pestilence.
	
	He shall defend thee under his wings, and thou shalt be safe under his fathers * his faithfulness and truth shall be thy shield and buckler.
	
	Thou shalt not be afraid for any terror by night * nor for the arrow with flieth by day.
	
	For the pestilence that walketh in darkness * nor for the sickness that destroyeth in the noonday.
	
	A thousand shall fall beside thee, and ten thousand at thy right hand * but it shall not come nigh thee.
	
	Yea, with thine eyes shalt thou behold * and see the reward of the ungodly.
	
	For thou, Lord, art my hope * thou hast set thine house of defense very high.
	
	There shall no evil happen unto thee * neither shall any plague come night thy dwelling.
	
	For he shall give his angels charge over thee * to keep thee in all thy ways.
	
	They shall bear thee in their hands * that thou hurt not thy foot against a stone.
	
	Thou shalt go upon the lion and adder * the young lion and the dragon shalt thou tread under thy feet.
	
	Because he hath set his love upon me, therefore will I deliver him * I will set him up, because he hath known my Name.
	
	He shall call upon me, and I will hear him * yea, I am with him in trouble; I will deliver him, and bring him to honor.
	
	With long life will I satisfy him * and shew him my salvation.
	
	\gloria{}
\end{multicols}