\instruct{Antiphons and psalms as on Second Vespers of the Nativity.}

\greannotation{\greformat{Resp.}}
\gregorioscore{propers/seasons/christmas/mary/first_vespers/resp.gabc}

\gresetinitiallines{0}
\veheading{A solus ortus cardine.}
\gregorioscore{propers/seasons/christmas/mary/first_vespers/hymn.gabc}

\begin{multicols}{2}
	\interlinepenalty=10000
	
	2. Blest author of this earthly frame,\\
	To take a servant's form he came,\\
	That, liberating flesh by flesh,\\
	Whom he had made might live afresh.
	
	3. In that chaste parent's holy womb\\
	Celestial grace hath found a home:\\
	And she, as earthly bride unknown,\\
	Yet calls that Offspring blest her own.
	
	4. The mansion of the modest breast\\
	Becomes a shrine where God shall rest:\\
	The pure and undefiled one\\
	Conceived in her womb the Son.
	
	5. Her time fulfill'd, that Son she bore,\\
	Whom Gabriel's voice had told afore:\\
	Whom, in his mother yet conceal'd,\\
	The infant Baptist had reveal'd.
	
	6. The manger and the straw he bore,\\
	The cradle did he not abhor:\\
	By milk the infant portions fed,\\
	Who gives e'en fowls their daily bread.
	
	7. The heav'nly chorus fill'd the sky,\\
	The Angels sang to God on high,\\
	What time to shepherds, watching lone,\\
	They made creation's Shepherd known.
	
	8. All honor, laud, and glory be,\\
	O Jesu, Virgin-born, to thee;\\
	All glory, as is ever meet,\\
	To Father and to Paraclete. Amen.
\end{multicols}

\gregorioscore{propers/circumcision/versicle.gabc}

\gresetinitiallines{1}
\greant{M}
\gregorioscore{propers/circumcision/magnificat.gabc}