\gresetinitiallines{1}
\greannotation{\greformat{Resp.}}
\gregorioscore{commons/lent/responsory.gabc}

\gresetinitiallines{0}
\veheading{Ex more docte mystico.}
\gregorioscore{commons/lent/hymn.gabc}

\begin{multicols}{2}
	\interlinepenalty=10000
	\raggedcolumns
	
	2. The law and seers that were of old\\
	In diverse ways this Lent foretold,\\
	Which Christ, all seasons' King and guide,\\
	In after ages sanctified.
	
	3. More sparing therefore let us make\\
	The words we speak, the food we take,\\
	Our sleep and mirth, and closer barred\\
	Be every sense in holy guard.
	
	4. Avoid the evil thoughts that roll\\
	Like waters o'er the heedless soul;\\
	Nor let te foe occasion find\\
	Our souls in slavery to bind.
	
	5. In prayer together let us fall,\\
	And cry for mercy, one and all,\\
	And weep before the Judge's feet,\\
	And his avenging wrath entreat.
	
	6. Thy grace have we offended sore,\\
	By sins, O Lord, which we deplore;\\
	But pour upon us from on high,\\
	O pardon One, thy mercy nigh.
	
	7. Remember thou, though frail we be,\\
	That yet thine handiwork are we;\\
	Nor let the honor of thy name\\
	By another put to shame.
	
	8. Forgive the sin that we have wrought;;\\
	Increase the good that we have sought;\\
	That we at length, our wanderings o'er,\\
	May please thee here and evermore.
	
	9. We pray thee, Holy Trinity,\\
	One God, unchanging Unity,\\
	That we from this our abstinence\\
	May reap the fruits of penitence. Amen.
\end{multicols}

\gregorioscore{commons/lent/versicle.gabc}