\gresetinitiallines{1}
\instruct{This antiphon is sung on all the psalms.}
\greannotation{\greformat{Ant.}}
\gregorioscore{commons/easter/vespers/antiphon.gabc}

\gresetinitiallines{0}
\veheading{Ad cenam agni.}
\veheading{Solemn Tone.}
\gregorioscore{commons/easter/vespers/hymn_solemn.gabc}

\veheading{Simple Tone.}
\gregorioscore{commons/easter/vespers/hymn_simple.gabc}

\begin{multicols}{2}
	\interlinepenalty=10000
	
	2. Upon the Altar of the Cross\\
	His Body hath redeemed our loss:\\
	And tasting of his roseate Blood,\\
	Our life is hid with him in God.
	
	3. That Paschal eve God's arm was bared:\\
	The devastating Angel spared:\\
	By strength of hand our hosts went free\\
	From Pharaoh's ruthless tyranny.
	
	4. Now Christ, our Paschal Lamb, is slain,\\
	The Lamb of God that knows no stain,\\
	The true oblation offered here,\\
	Our own unleavened Bread sincere.
	
	5. O thou from whom hell's monarch flies,\\
	O great, O very sacrifice,\\
	Thy captive people are set free,\\
	And endless life restored in thee.
	
	6. For Christ, arising from the dead,\\
	From conquered hell victorious sped:\\
	He thrusts the tyrant down to chains.\\
	And Paradise for man regains.
	
	7. We pray thee, King with glory decked,\\
	In this our Paschal joy, protect\\
	From all that death would fain effect,\\
	Thy ransomed flock, thine own elect.
	
	8. To thee who, dead, again dost live,\\
	All glory, Lord, thy people give:\\
	All glory, as is ever meet,\\
	To Father and to Paraclete. Amen.
\end{multicols}

\gregorioscore{commons/easter/first_vespers/versicle.gabc}