\gresetinitiallines{1}
\greant{1}
\gregorioscore{propers/seasons/christmas/nativity/vespers/1.gabc}

\input{psalter/113}

\greant{2}
\gregorioscore{propers/seasons/christmas/nativity/vespers/2.gabc}

\input{psalter/117}

\greant{3}
\gregorioscore{propers/seasons/christmas/nativity/vespers/3.gabc}

\input{psalter/146}

\greant{4}
\gregorioscore{propers/seasons/christmas/nativity/vespers/4.gabc}

\input{psalter/147i}

\greant{5}
\gregorioscore{propers/seasons/christmas/nativity/vespers/5.gabc}

\instruct{These three psalms are sung under the same antiphon.}

\input{psalter/148}

\input{psalter/149}

\input{psalter/150}

\greannotation{\greformat{Resp.}}
\gregorioscore{propers/seasons/christmas/nativity/vespers/resp.gabc}

\veheading{arg1}
\gresetinitiallines{0}
\gregorioscore{propers/seasons/christmas/nativity/vespers/hymn.gabc}

\begin{multicols}{2}
	\interlinepenalty=10000
	
	2. Begotten of no human will,\\
	But of the Spirit, thou art still\\
	The Word of God in flesh arrayed,\\
	The promised fruit to man displayed.
	
	3. The virgin womb that burden gained\\
	With virgin honor all unstained;\\
	The banners there to virtue glow;\\
	God in his temple dwells below.
	
	4. Forth from his chamber goeth he,\\
	That royal home of purity,\\
	A giant in twofold substance one,\\
	Rejoicing now his course to run.
	
	5. From God the Father he proceeds,\\
	To God the Father back he speeds;\\
	His course he runs to death and hell,\\
	Returning on God's throne to dwell.
	
	6. O equal to thy Father, thou!\\
	Gird on thy fleshly mantle now;\\
	The weakness of our mortal state\\
	With deathless might invigorate.
	
	7. Thy cradle here shall glitter bright,\\
	and darkness breathe a newer light,\\
	Where endless faith shall shine serene,\\
	And twilight never intervene.
	
	8. All laud to God the Father be;\\
	All praise, eternal Son, to thee:\\
	All glory, as is ever meet,\\
	To God the Holy Paraclete. Amen.
\end{multicols}

\gregorioscore{propers/seasons/christmas/nativity/vespers/versicle.gabc}

\gresetinitiallines{1}
\greant{M}
\gregorioscore{propers/seasons/christmas/nativity/vespers/magnificat.gabc}